\newpage

\begin{thebibliography}{99}


  \bibitem{method}
  \textit{N.\,Nikitin}, Finite-difference method for incompressible Navier–Stokes equations in 
  arbitrary orthogonal curvilinear coordinates // J. Comput. Phys. 217 (2006) 759–781.

  \bibitem{lin-stability}
  \textit{Etienne Non, Roger Pierre, and Jean-Jacques Gervais}, Linear stability of the 
  three-dimensional lid-driven cavity // Physics of Fluids 18, 084103 (2006)

  \bibitem{RK}
	\textit{Nikitin N.} Third--order--accurate semi--implicit Runge--Kutta scheme for incompressible Navier--Stokes equations //International journal for numerical methods in fluids.~---~2006.~---~Т. 51.~---~№. 2.~---~С. 221--233.
  
  \bibitem{introduction}
   \textit{Ramanan\.N., Homsy\.G.\.M.} Linear stability of lid-driven cavity flow 
  //Physics of Fluids.~--- 1994.~--- Т. 6.~--- С. 2690.
  
  \bibitem{2DBench}
   \textit{Erturk\.E., Corke\.T.\.C., Gökçöl\.C.} Numerical solutions of 2-D steady incompressible
  driven cavity flow at high Reynolds numbers //International Journal for Numerical Methods in 
  Fluids.~--- 2005.~--- Т. 48.~--- №. 7.~--- С. 747--774.

	\bibitem{KimMoin}
	\textit{J.~Kim and P.~Moin}, Application of a fractional step method to incompressible Navier-Stokes equations//
 J.~Comput.~Phys. 59, 308 (1985).

  \bibitem{betyaev}
   \textit{Бетяев~С.К.} Пролегомены к // РХД, 2006 г. 304 стр
  
  \bibitem{wiki}
   Материал из Википедии~--- свободной энциклопедии [ru.wikipedia.org]

  \bibitem{history}
   История гидродинамики, опубликованно 29-го января 2009 г [http://iproc.ru/interesting/hydro-history]

\end{thebibliography}
